Introduction to Olavo de Carvalho´s Work

### 2019-02-13 texts/philosophy/introolavo.tex
.

	Um método é um conjunto de proposições auto-evidentes (ou provadas com base nelas) que delimitam um objeto e os meios de conhecê-lo.
	O bom método não define o seu objeto, mas recebe essa definição de uma prévia descrição fenomenológica.
	\section{Philosopher Maturity}
	\subsection{Impression of Reality}
	\subsubsection{Senses}
	\subsubsection{Limited Structure of the Reality}
	Kantism is not a philosophy. It`s a practical joke.
	Kant had to be VERY stupid to not understand that our apprehending only the phenomenic appearances, and not the thing in itself, is not a limitation in us, but of the things in themselves. If he had noticed this, he would have realized that his theory DOES NOT MEAN ANYTHING.
	All modern science is based on a phenomenist metaphysics, in which there are no real beings, just measurable appearances. It is so because no real entity is exhausted on which a science, or all of them together, can say about it. Besides, each one only asks questions about the object that pertain to its own methodology and not about the ontological structure of the object itself. This structure remains outside the reach of each science in particular and cannot be reengineered by the mere articulation of a number of the sciences. The experience of REALITY is an anterior necessity for the possibility of any science, which they just complement with specific details. This same experience of reality remains outside of epistemological control of any science.
	No scientific explanation refers to the fact in itself, as small as it may be, and even less accounts for its causes. It just highlights the aspects of the fact that correspond to the methodological perspective of that science in particular. "Reality" is entirely out of all that. Ninety-nine point ninety-nine percent of science professionals ignore that this is how things are.
	Practicing any science without the constant critical examination of its epistemological pillars, and therefore of its own limitations, causes a state of hypnotic hallucination. In such a state the person denies the validity of his spontaneous perception of things - which is the foundation of any science - and substitutes it for some hypothetical system that gives him the impression of being scientific. Many scientists end up becoming like Felix, the Cat ( https://www.youtube.com/watch?v=amGbBFsiuzc ), living in a world drawn by themselves.
	When a science professor says there is no significant genetic differences between a monkey and a three-year-old, he imagines that this difference really does not exist, and not that it is his genetic perspective that is insufficient to apprehend it.
	Ultimately, the sciences as they exist today are not meant to know the world, but to fabricate it as an industrialized product.
	Olavo de Carvalho
	\subsection{Unification}
	\subsubsection{Reality Unification}
	\subsubsection{Conscience Unification}
	\subsubsection{12 layers of personality}

@@

>>>>

	Um método é um conjunto de proposições auto-evidentes (ou provadas com base nelas) que delimitam um objeto e os meios de conhecê-lo.
	O bom método não define o seu objeto, mas recebe essa definição de uma prévia descrição fenomenológica.
	\section{Philosopher Maturity}
	\subsection{Impression of Reality}
	\subsubsection{Senses}
	\subsubsection{Limited Structure of the Reality}
	Kantism is not a philosophy. It`s a practical joke.
	Kant had to be VERY stupid to not understand that our apprehending only the phenomenic appearances, and not the thing in itself, is not a limitation in us, but of the things in themselves. If he had noticed this, he would have realized that his theory DOES NOT MEAN ANYTHING.
	All modern science is based on a phenomenist metaphysics, in which there are no real beings, just measurable appearances. It is so because no real entity is exhausted on which a science, or all of them together, can say about it. Besides, each one only asks questions about the object that pertain to its own methodology and not about the ontological structure of the object itself. This structure remains outside the reach of each science in particular and cannot be reengineered by the mere articulation of a number of the sciences. The experience of REALITY is an anterior necessity for the possibility of any science, which they just complement with specific details. This same experience of reality remains outside of epistemological control of any science.
	No scientific explanation refers to the fact in itself, as small as it may be, and even less accounts for its causes. It just highlights the aspects of the fact that correspond to the methodological perspective of that science in particular. "Reality" is entirely out of all that. Ninety-nine point ninety-nine percent of science professionals ignore that this is how things are.
	Practicing any science without the constant critical examination of its epistemological pillars, and therefore of its own limitations, causes a state of hypnotic hallucination. In such a state the person denies the validity of his spontaneous perception of things - which is the foundation of any science - and substitutes it for some hypothetical system that gives him the impression of being scientific. Many scientists end up becoming like Felix, the Cat ( https://www.youtube.com/watch?v=amGbBFsiuzc ), living in a world drawn by themselves.
	When a science professor says there is no significant genetic differences between a monkey and a three-year-old, he imagines that this difference really does not exist, and not that it is his genetic perspective that is insufficient to apprehend it.
	Ultimately, the sciences as they exist today are not meant to know the world, but to fabricate it as an industrialized product.
	Olavo de Carvalho
	\subsection{Unification}
	\subsubsection{Reality Unification}

	INTUICIONISMO RADICAL
	por Olavo de Carvalho

	?Intuição é conhecimento imediato, isto é, sem intermediações. Se ela não existisse, não existiria conhecimento nenhum, pois o conhecimento dos intermediários precisaria de outros intermediários, e estes de outros ainda, e assim por diante ilimitadamente. Se falamos, por exemplo, da intuição sensível, dizer ? a sério, e não como mera abreviatura verbal ? que só conhecemos os objetos do mundo físico "por intermédio" dos sentidos, portanto não diretamente, é como dizer que uma arma de fogo não atira diretamente mas "por intermédio" do cano, como se o cano não fosse parte dela e sim um ajudante externo; pior ainda, além dos sentidos não temos nenhum outro órgão capaz de captar as qualidades sensíveis, de modo que, se os sentidos fossem apenas "intermediários", estariam mediando entre os objetos sensíveis e um nada.

	Quando apreendemos a conclusão de um silogismo, essa apreensão é também direta e intuitiva, caso contrário precisaríamos de um intermediário entre nós e essa conclusão, e esse intermediário precisaria de outro, etc. etc.

	A intuição é a apreensão de uma evidência. Evidência é presença imediata à consciência, o correlato objetivo da intuição. O que é evidente não requer prova. Prova é evidência indireta, ou deficiente, obtida por uma articulação de representações mentais. Quando atinamos com a veracidade de uma prova lógica, temos a apreensão intuitiva só da prova enquanto tal, não dos objetos correspondentes.

	Só a intuição é critério cabal da verdade, seja na apreensão dos dados sensíveis, seja no próprio raciocínio lógico.

	Quem diz que algum conhecimento bem provado é "contra-intuitivo" usa a palavra "intuição" para designar a simples expectativa de uma percepção possível; dito de outro modo, uma crença do senso comum sem intuição nenhuma.

	É isso o que eu chamo ?intuicionismo radical?.?
	https://www.facebook.com/photo.php?fbid=10215093755150845&set=a.3036833753418&type=3&theater

	\subsubsection{Conscience Unification}
	\subsubsection{12 layers of personality}

@@

	Já expliquei mil vezes que a ciência política começou quando Platão e Aristóteles criaram a distinção entre o discurso do agente político e o do observador científico. A objetividade das opiniões do cientista político não vem de nenhum isentismo, mas do simples fato de ele JAMAIS se rebaixar à função de porta-voz de um grupo político. É a minha total independência de quaisquer grupos que me torna incompreensível e escandaloso para muita gente num pais em que praticamente TODO pensamento é grupal.

	https://www.facebook.com/olavo.decarvalho/posts/10156896956572192
